%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://www.upc.edu/en}{UPC (Polytechnic University of Catalonia)}} % Job title
    {Assistant Professor} % Organization
    {Sep 2021 – Currently} % Date(s)
    {Barcelona} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Courses: \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/BD}{Introduction to Databases}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://getquokka.app/}{Not So Dark}} % Job title
    {Lead Front-End Developer} % Organization
    {Nov 2020 – Currently (9 mos)} % Date(s)
    {Barcelona/Paris} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of the main web and mobile app with VueJS 2. Leading a team of 3 developers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.myreach.io}{REACH}} % Organization
    {Full-Stack Developer} % Job title
    {Nov 2018 – Sep 2020 (1 yr 11mos)} % Date(s)
    {Barcelona} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed the main web application, as well as the internal management web app. Both with Angular 9.}
        \item {Implemented part of the API in Node.js (Express and Typescript), specifically some of the main PostgreSQL models and CRUD functionalities.}
        \item {Direction of the final degree project "3D visualization of a graph-based file system", by Raúl Ibáñez Pérez.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.asesacademia.com}{ASES Acadèmia}} % Organization
    {Professor} % Job title
    {Feb 2016 – Jan 2020 (4 yrs)} % Date(s)
    {Barcelona} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Computer Science courses: \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/FM}{Math fundamentals}, \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/M1}{Maths 1}, \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/M2}{Maths 2}, \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/PRO1}{Programming 1}, \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/PRO2}{Programming 2} and \href{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/EDA}{Data Structures and Algorithms}.}
        \item {Instructed groups of up to 35 students. Created my own teaching material for students (dossiers that integrate both theory and problems).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://philinks.com}{Philinks}} % Organization
    {Front-End Developer} % Job title
    {Nov 2018 – Jan 2019 (3 mos)} % Date(s)
    {Barcelona} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of the DIEC (Dictionary of the Catalan Studies Institute)  webapp: \url{https://dlc.iec.cat}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://inlab.fib.upc.edu/ca}{inLab FIB (CS School - UPC)}} % Organization
    {Software Engineer Intern} % Job title
    {May 2016 – Jun 2018 (2yrs 2mos)} % Date(s)
    {Barcelona} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Main developer of the new FIB Alumni web portal: \url{fibalumni.net}; and Festibity’s web portal: \url{festibity.com}. Both with Drupal 7 and PHP.}
        \item {Developer of Quadrivia: Trivial style Android app for UOC students. Implemented new functionalities and test modes.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
%---------------------------------------------------------